Supplementary materials for Comparative safety and effectiveness of Pfizer BA.4-5 versus Sanofi during the Spring 2023 COVID-19 booster vaccination programme in England

### 2024-02-27 write-up/manuscript/manuscript.qmd

We considered three effectiveness outcomes. COVID-19 hospital admission was identified using Secondary Use Service (SUS) in-patient hospital spell records with International Statistical Classification of Diseases and Related Health Problems 10th Revision (ICD-10) codes U07.1, U07.2, or U.109 as the primary or non-primary reason for admission. COVID-19 critical care admissions were any COVID-19 hospital spell with at least one day spent in critical care (including any such spells occurring subsequent to the first spell after vaccination). COVID-19 death was defined as COVID-19 ICD-10 codes (as before) mentioned anywhere on the death certificate (i.e., as an underlying or contributing cause of death). We also report on non-COVID-19 deaths.

@@

We identified `r label_number(1, big.mark=",")(filter(rst$cv$flowchart_totals, boost_type=="any") %>% pull(n) %>% sum())` people in the CV cohort, and of these `r label_number(1, big.mark=",")(filter(rst$cv$flowchart_totals, boost_type=="pfizerBA45") %>% pull(n))` (`r label_percent(0.1)(filter(rst$cv$flowchart_totals, boost_type=="pfizerBA45") %>% pull(pct))`) received Pfizer BA.4-5 and `r label_number(1, big.mark=",")(filter(rst$cv$flowchart_totals, boost_type=="sanofi") %>% pull(n))` (`r label_percent(0.1)(filter(rst$cv$flowchart_totals, boost_type=="sanofi") %>% pull(pct))`) received Sanofi, with `r label_number(1, big.mark=",")(filter(rst$cv$flowchart, crit=="c4", boost_type=="pfizerBA45") %>% pull(n))` (`r label_percent(0.1)(filter(rst$cv$flowchart, crit=="c4", boost_type=="pfizerBA45") %>% pull(pct_all))`) and `r label_number(1, big.mark=",")(filter(rst$cv$flowchart, crit=="c4", boost_type=="sanofi") %>% pull(n))` (`r label_percent(0.1)(filter(rst$cv$flowchart, crit=="c4", boost_type=="sanofi") %>% pull(pct_all))`) eligible for matching respectively (Figure 1a).

`r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart_totals, boost_type=="any") %>% pull(n) %>% sum())` people were in the 75+ cohort, and of these `r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart_totals, boost_type=="pfizerBA45") %>% pull(n))` (`r label_percent(0.1)(filter(rst$age75plus$flowchart_totals, boost_type=="pfizerBA45") %>% pull(pct))`) received Pfizer BA.4-5 and `r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart_totals, boost_type=="sanofi") %>% pull(n))` (`r label_percent(0.1)(filter(rst$age75plus$flowchart_totals, boost_type=="sanofi") %>% pull(pct))`) received Sanofi, with `r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart, crit=="c4", boost_type=="pfizerBA45") %>% pull(n))` (`r label_percent(0.1)(filter(rst$age75plus$flowchart, crit=="c4", boost_type=="pfizerBA45") %>% pull(pct_all))`) and `r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart, crit=="c4", boost_type=="sanofi") %>% pull(n))` (`r label_percent(0.1)(filter(rst$age75plus$flowchart, crit=="c4", boost_type=="sanofi") %>% pull(pct_all))`) eligible for matching respectively (Figure 1b).

@@

@@

IRRs in the 16-week period after vaccination were `r rst$age75plus$contrasts_table %>% filter(outcome=="covidadmitted", subgroup=="all") %>% pull(irrCI_95)` for COVID-19 hospital admission, `r rst$age75plus$contrasts_table %>% filter(outcome=="covidcritcare", subgroup=="all") %>% pull(irrCI)` for COVID-19 critical care admission, `r rst$age75plus$contrasts_table %>% filter(outcome=="coviddeath", subgroup=="all") %>% pull(irrCI)` for COVID-19 death, and `r rst$age75plus$contrasts_table %>% filter(outcome=="noncoviddeath", subgroup=="all") %>% pull(irrCI)` for non-COVID-19 death (Figure 3).

@@

#### Figure 1a: Flow of participants into the CV cohort

![figure1a](figures_manual/flowchart_cv.png){width="60%"}

#### Figure 1b: Flow of participants into the 75+ cohort

@@

```{r}
#| label: function-ci
#| warning: false
#| out.width: '100%'
#| out.height: '50%'

@@

  plot_combined <- patchwork::wrap_plots(
    plot_ci#, 
    #plot_rd, 
    #plot_rr, 
    #plot_irr,
    #ncol=2,
    #widths=c(n_subgroups,1)
  )

@@

```{r figure-ci-all}
#| echo: false

@@

```{r figure-ci-age75plus-all}
#| echo: false
#| warning: false
#| out-width: '100%'
#| out-height: '80%'

@@

write_csv(contrasts_jasper_plot, fs::path(output_dir_qmd,"irr_plots.csv"),na="")

# Run Jasper IRR plot script (requires https://github.com/arnhew99/Jasper?tab=readme-ov-file#jasper)
#source(here::here("write-up", "manuscript", "irr_plots_jasper_code.r"))

plot_irr_lines <- contrasts_plot %>%
  ggplot(aes(y=outcome_descr)) +
  geom_vline(aes(xintercept=1), linetype="dotted", colour="darkgrey")+
   geom_point(aes(x=irr), position=position_dodge(width=0.1))+
  geom_linerange(aes(xmin=irr.ll, xmax=irr.ul), position=position_dodge(width=0.1))+
  #facet_grid(rows=vars(outcome_descr), scales="free", space="free_y", switch="y")+
  facet_wrap(vars(cohort_descr), scales="free_y", ncol=1, strip.position = "top")+
  scale_x_log10(label=label_number(0.1, style_negative="minus", big.mark=","),n.breaks =8, oob=~oob_squish(.,range=log(c(0.2,8), 10)), expand=expansion())+
  #scale_fill_brewer(type="qual", palette="Set2")+
  scale_fill_manual(values=c("transparent", "darkgrey"))+
  labs(
    #subtitle="\n\n\nIncidence Rate Ratios",
    x="<- favours Sanofi  |  favours Pfizer BA.4-5 ->",
    y=NULL
  )+
  theme_minimal()+
  theme(
    plot.margin=grid::unit(c(0,0,0,0), "mm"),
    plot.subtitle=element_text(hjust=0.5, vjust=0),
    legend.position="none",
    #panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    #strip.background = element_blank(),
    #strip.placement="outside",
    strip.text = element_text(hjust=0),
    #strip.text.y.left = element_text(angle=0),
    #strip.text.y.left = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(0.4, "lines"),
  )

plot_irr_table <- contrasts_plot %>%
  ggplot(aes(y=outcome_descr)) +
  geom_text(aes(x=0.5, label=irrCI), hjust=0.5, vjust=0.5, size=9/.pt)+
  #geom_rect(aes(ymin=rownum-0.5, ymax=rownum+0.5, xmin=0.2, xmax=0.8, fill=patch), alpha=0.2)+
  facet_wrap(vars(cohort_descr), scales="free_y", ncol=1, strip.position = "top")+
  scale_fill_manual(values=c("transparent", "darkgrey"))+
  scale_x_continuous(expand=expansion())+
  #labs(subtitle="\nIncidence\nRate Ratio\n(95% CI)")+
  theme_minimal()+
  theme(
    plot.margin=grid::unit(c(0,0,0,0), "mm"),
    plot.subtitle=element_text(hjust=0.5, vjust=0),
    legend.position="none",
    panel.grid = element_blank(),
    strip.text =element_text(colour="transparent"),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.x = element_blank(),
    axis.title.x=element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(0.5, "lines"),
  )+
  NULL

@@

  plot_combined <- patchwork::wrap_plots(
    plot_irr_lines,
    plot_irr_table,
    ncol=2,
    widths=c(2,0.9)
  )

  ggsave(
    filename=glue("irr_pvals.jpeg"),
    path=output_dir_qmd,
    plot=plot_combined,
    width=20, height=15, units="cm"
  )

>>>>

We considered three effectiveness outcomes. COVID-19 hospital admission was identified using Secondary Use Service (SUS) in-patient hospital spell records with International Statistical Classification of Diseases and Related Health Problems 10th Revision (ICD-10) codes U07.1, U07.2, or U.109 as the primary or non-primary reason for admission. COVID-19 critical care admissions were any COVID-19 hospital spell with at least one day spent in critical care (including any such spells occurring subsequent to the first spell after vaccination). COVID-19 death was defined as COVID-19 ICD-10 codes (as before) mentioned anywhere on the death certificate (i.e., as an underlying or contributing cause of death). We also report on non-COVID-19 deaths.
We considered three effectiveness outcomes. COVID-19 hospital admission was identified using Secondary Use Service (SUS) in-patient hospital spell records with International Statistical Classification of Diseases and Related Health Problems 10th Revision (ICD-10) codes U07.1, U07.2, or U.109 as the primary or non-primary reason for admission. COVID-19 critical care admissions were any COVID-19 hospital spell with at least one day spent in critical care (including any such spells occurring subsequent to the first spell after vaccination). COVID-19 death was defined as COVID-19 ICD-10 codes (as before) mentioned anywhere on the death certificate (i.e., as an underlying or contributing cause of death). We also report on non-COVID-19 deaths.

@@

We identified `r label_number(1, big.mark=",")(filter(rst$cv$flowchart_totals, boost_type=="any") %>% pull(n) %>% sum())` people in the CV cohort, and of these `r label_number(1, big.mark=",")(filter(rst$cv$flowchart_totals, boost_type=="pfizerBA45") %>% pull(n))` (`r label_percent(0.1)(filter(rst$cv$flowchart_totals, boost_type=="pfizerBA45") %>% pull(pct))`) received Pfizer BA.4-5 and `r label_number(1, big.mark=",")(filter(rst$cv$flowchart_totals, boost_type=="sanofi") %>% pull(n))` (`r label_percent(0.1)(filter(rst$cv$flowchart_totals, boost_type=="sanofi") %>% pull(pct))`) received Sanofi, with `r label_number(1, big.mark=",")(filter(rst$cv$flowchart, crit=="c4", boost_type=="pfizerBA45") %>% pull(n))` (`r label_percent(0.1)(filter(rst$cv$flowchart, crit=="c4", boost_type=="pfizerBA45") %>% pull(pct_all))`) and `r label_number(1, big.mark=",")(filter(rst$cv$flowchart, crit=="c4", boost_type=="sanofi") %>% pull(n))` (`r label_percent(0.1)(filter(rst$cv$flowchart, crit=="c4", boost_type=="sanofi") %>% pull(pct_all))`) eligible for matching respectively (Figure 1a).
We identified `r label_number(1, big.mark=",")(filter(rst$cv$flowchart_totals, boost_type=="any") %>% pull(n) %>% sum())` people in the CV cohort, and of these `r label_number(1, big.mark=",")(filter(rst$cv$flowchart_totals, boost_type=="pfizerBA45") %>% pull(n))` (`r label_percent(0.1)(filter(rst$cv$flowchart_totals, boost_type=="pfizerBA45") %>% pull(pct))`) received Pfizer BA.4-5 and `r label_number(1, big.mark=",")(filter(rst$cv$flowchart_totals, boost_type=="sanofi") %>% pull(n))` (`r label_percent(0.1)(filter(rst$cv$flowchart_totals, boost_type=="sanofi") %>% pull(pct))`) received Sanofi, with `r label_number(1, big.mark=",")(filter(rst$cv$flowchart, crit=="c4", boost_type=="pfizerBA45") %>% pull(n))` (`r label_percent(0.1)(filter(rst$cv$flowchart, crit=="c4", boost_type=="pfizerBA45") %>% pull(pct_all))`) and `r label_number(1, big.mark=",")(filter(rst$cv$flowchart, crit=="c4", boost_type=="sanofi") %>% pull(n))` (`r label_percent(0.1)(filter(rst$cv$flowchart, crit=="c4", boost_type=="sanofi") %>% pull(pct_all))`) eligible for matching respectively (Figure 1a).

`r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart_totals, boost_type=="any") %>% pull(n) %>% sum())` people were in the 75+ cohort, and of these `r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart_totals, boost_type=="pfizerBA45") %>% pull(n))` (`r label_percent(0.1)(filter(rst$age75plus$flowchart_totals, boost_type=="pfizerBA45") %>% pull(pct))`) received Pfizer BA.4-5 and `r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart_totals, boost_type=="sanofi") %>% pull(n))` (`r label_percent(0.1)(filter(rst$age75plus$flowchart_totals, boost_type=="sanofi") %>% pull(pct))`) received Sanofi, with `r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart, crit=="c4", boost_type=="pfizerBA45") %>% pull(n))` (`r label_percent(0.1)(filter(rst$age75plus$flowchart, crit=="c4", boost_type=="pfizerBA45") %>% pull(pct_all))`) and `r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart, crit=="c4", boost_type=="sanofi") %>% pull(n))` (`r label_percent(0.1)(filter(rst$age75plus$flowchart, crit=="c4", boost_type=="sanofi") %>% pull(pct_all))`) eligible for matching respectively (Figure 1b).
`r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart_totals, boost_type=="any") %>% pull(n) %>% sum())` people were in the 75+ cohort, and of these `r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart_totals, boost_type=="pfizerBA45") %>% pull(n))` (`r label_percent(0.1)(filter(rst$age75plus$flowchart_totals, boost_type=="pfizerBA45") %>% pull(pct))`) received Pfizer BA.4-5 and `r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart_totals, boost_type=="sanofi") %>% pull(n))` (`r label_percent(0.1)(filter(rst$age75plus$flowchart_totals, boost_type=="sanofi") %>% pull(pct))`) received Sanofi, with `r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart, crit=="c4", boost_type=="pfizerBA45") %>% pull(n))` (`r label_percent(0.1)(filter(rst$age75plus$flowchart, crit=="c4", boost_type=="pfizerBA45") %>% pull(pct_all))`) and `r label_number(1, big.mark=",")(filter(rst$age75plus$flowchart, crit=="c4", boost_type=="sanofi") %>% pull(n))` (`r label_percent(0.1)(filter(rst$age75plus$flowchart, crit=="c4", boost_type=="sanofi") %>% pull(pct_all))`) eligible for matching respectively (Figure 1b).

@@

````{comment}
````{comment}

````
````

@@

IRRs in the 16-week period after vaccination were `r rst$age75plus$contrasts_table %>% filter(outcome=="covidadmitted", subgroup=="all") %>% pull(irrCI_95)` for COVID-19 hospital admission, `r rst$age75plus$contrasts_table %>% filter(outcome=="covidcritcare", subgroup=="all") %>% pull(irrCI)` for COVID-19 critical care admission, `r rst$age75plus$contrasts_table %>% filter(outcome=="coviddeath", subgroup=="all") %>% pull(irrCI)` for COVID-19 death, and `r rst$age75plus$contrasts_table %>% filter(outcome=="noncoviddeath", subgroup=="all") %>% pull(irrCI)` for non-COVID-19 death (Figure 3).
IRRs in the 16-week period after vaccination were `r rst$age75plus$contrasts_table %>% filter(outcome=="covidadmitted", subgroup=="all") %>% pull(irrCI_95)` for COVID-19 hospital admission, `r rst$age75plus$contrasts_table %>% filter(outcome=="covidcritcare", subgroup=="all") %>% pull(irrCI)` for COVID-19 critical care admission, `r rst$age75plus$contrasts_table %>% filter(outcome=="coviddeath", subgroup=="all") %>% pull(irrCI)` for COVID-19 death, and `r rst$age75plus$contrasts_table %>% filter(outcome=="noncoviddeath", subgroup=="all") %>% pull(irrCI)` for non-COVID-19 death (Figure 3).

@@

#### Figure 1a: Flow of participants into the CV cohort
#### Figure 1a: Flow of participants into the CV cohort

![figure1a](figures_manual/flowchart_cv.png){width="60%"}
![figure1a](figures_manual/flowchart_cv.png){width="60%"}

#### Figure 1b: Flow of participants into the 75+ cohort
#### Figure 1b: Flow of participants into the 75+ cohort

@@

```{r}
#| label: function-ci
#| warning: false
#| warning: false
#| out.width: '100%'
#| out.height: '50%'

@@

  plot_combined <- patchwork::wrap_plots(
    plot_ci#, 
    plot_ci#, 
    #plot_rd, 
    #plot_rr, 
    #plot_irr,
    #ncol=2,
    #widths=c(n_subgroups,1)
    #plot_irr,
    #ncol=2,
    #widths=c(n_subgroups,1)
  )

@@

```{r figure-ci-cv-all}
#| echo: false

@@

```{r figure-ci-age75plus-all}
#| echo: false
#| warning: false
#| out-width: '100%'
#| out-height: '80%'
#| out-height: '80%'

@@

write_csv(contrasts_jasper_plot, fs::path(output_dir_qmd,"irr_plots.csv"),na="")
write_csv(contrasts_jasper_plot, fs::path(output_dir_qmd,"irr_plots.csv"),na="")

# Run Jasper IRR plot script (requires https://github.com/arnhew99/Jasper?tab=readme-ov-file#jasper)
#source(here::here("write-up", "manuscript", "irr_plots_jasper_code.r"))
#source(here::here("write-up", "manuscript", "irr_plots_jasper_code.r"))

plot_irr_lines <- contrasts_plot %>%
  ggplot(aes(y=outcome_descr)) +
  geom_vline(aes(xintercept=1), linetype="dotted", colour="darkgrey")+
   geom_point(aes(x=irr), position=position_dodge(width=0.1))+
  geom_linerange(aes(xmin=irr.ll, xmax=irr.ul), position=position_dodge(width=0.1))+
  #facet_grid(rows=vars(outcome_descr), scales="free", space="free_y", switch="y")+
  facet_wrap(vars(cohort_descr), scales="free_y", ncol=1, strip.position = "top")+
  scale_x_log10(label=label_number(0.1, style_negative="minus", big.mark=","),n.breaks =8, oob=~oob_squish(.,range=log(c(0.2,8), 10)), expand=expansion())+
  #scale_fill_brewer(type="qual", palette="Set2")+
  scale_fill_manual(values=c("transparent", "darkgrey"))+
  labs(
    #subtitle="\n\n\nIncidence Rate Ratios",
    #subtitle="\n\n\nIncidence Rate Ratios",
    x="<- favours Sanofi  |  favours Pfizer BA.4-5 ->",
    y=NULL
  )+
  theme_minimal()+
  theme(
    plot.margin=grid::unit(c(0,0,0,0), "mm"),
    plot.subtitle=element_text(hjust=0.5, vjust=0),
    legend.position="none",
    #panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    #strip.background = element_blank(),
    #strip.placement="outside",
    strip.text = element_text(hjust=0),
    #strip.text.y.left = element_text(angle=0),
    #strip.text.y.left = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(0.4, "lines"),
    panel.spacing = unit(0.4, "lines"),
  )

plot_irr_table <- contrasts_plot %>%
  ggplot(aes(y=outcome_descr)) +
  geom_text(aes(x=0.5, label=irrCI), hjust=0.5, vjust=0.5, size=9/.pt)+
  #geom_rect(aes(ymin=rownum-0.5, ymax=rownum+0.5, xmin=0.2, xmax=0.8, fill=patch), alpha=0.2)+
  facet_wrap(vars(cohort_descr), scales="free_y", ncol=1, strip.position = "top")+
  scale_fill_manual(values=c("transparent", "darkgrey"))+
  scale_x_continuous(expand=expansion())+
  #labs(subtitle="\nIncidence\nRate Ratio\n(95% CI)")+
  theme_minimal()+
  theme(
    plot.margin=grid::unit(c(0,0,0,0), "mm"),
    plot.subtitle=element_text(hjust=0.5, vjust=0),
    legend.position="none",
    panel.grid = element_blank(),
    strip.text =element_text(colour="transparent"),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.x = element_blank(),
    axis.title.x=element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(0.4, "lines"),
  )+
  NULL

@@

  plot_combined <- patchwork::wrap_plots(
    plot_irr_lines,
    plot_irr_table,
    ncol=2,
    widths=c(2,0.9)
    ncol=2,
    widths=c(2,0.9)
  )

  ggsave(
    filename=glue("irr_pvals.jpeg"),
    path=output_dir_qmd,
    plot=plot_combined,
    width=20, height=15, units="cm"
    width=20, height=15, units="cm"
  )

### 2024-02-27 write-up/manuscript/supplement.qmd

  plot_smd
}

@@

#### Figure S2a: Standardised Mean Differences for CV cohort between Pfizer BA.4-5 and Sanofi groups, before and after matching
```{r}
#| label: figure-smd-cv
#| out-width: '90%'
#| out-height: '100%'
#| output: asis
#| out-extra: ''

@@

#### Figure S2b: Standardised Mean Differences for 75+ cohort between Pfizer BA.4-5 and Sanofi groups, before and after matching
```{r}
#| label: figure-smd-age75plus
#| out-width: '90%'
#| out-height: '100%'
#| output: asis
#| out-extra: ''

>>>>

  plot_smd

  ggsave(
    filename=glue("smd_{.cohort}.jpeg"),
    path=output_dir_qmd,
    plot=plot_smd,
    width=20, height=20, units="cm"
  )
}

@@

#### Figure S2a: Standardised Mean Differences for CV cohort between Pfizer BA.4-5 and Sanofi groups, before and after matching
```{r}
#| label: figure-smd-cv
#| out-width: '90%'
#| out-height: '200%'
#| output: asis
#| out-extra: ''

@@

#### Figure S2b: Standardised Mean Differences for 75+ cohort between Pfizer BA.4-5 and Sanofi groups, before and after matching
```{r}
#| label: figure-smd-age75plus
#| out-width: '90%'
#| out-height: '200%'
#| output: asis
#| out-extra: ''
